### 2009-08-07 trunk/papers/SBMF2009/Presentation/content/5_Proofs.tex
version almost conclused

\section{Prove Process}

\begin{frame}
\frametitle{Prove Process of Projects}

@@

   \item  Approximately 25\% are not solved automatically
	\item  Approximately 18 days are needed to make almost all the proofs using a monolithic computer
		\begin{itemize}
			\item But You can reduce this time if you use several computer to prove
		\end{itemize}
	\item  Sometimes was needed  replay the proofs when were needed news fixes
\end{itemize}

@@

\begin{frame}
\frametitle{A example of user pass}

\begin{itemize}
   \item Specialized:
   \item \ldots
   \item Generally:
\end{itemize}

>>>>

\section{Proof Process}

\begin{frame}
\frametitle{Proof Process of Projects}

@@

   \item  Approximately 25\% are not solved automatically
	\item Approximately 18 days are needed to make almost all the proofs using a monolithic computer
	\item Some proofs needed to be replayed when we make changes to the specification
	\item The proof's time can be reduced using advanced features

\end{itemize}

@@

\begin{frame}
\frametitle{Proof Process - Advanced Features}

	\begin{itemize}
	\item Parallel theorem prover with 3 dual core computers 
	\item Two simple examples of user pass from theorem prover

 		\begin{itemize}
 		   \item Specific:\\
 		  	 $Pattern( x , y : dom(bitget) )$ \\ $\& ff(0) \& dd \& eh(dom(bitget)) \& ss \& pr;$\\
 		    \ldots
 		   \item General:\\
 		   	$Pattern( x : dom(y) )$ \\ $\& ff(0) \& dd \& eh(dom(y)) \& ss \& pr;$
         \end{itemize}

    \end{itemize}
